Policy Costs

### 2013-10-31 inst/doc/policycosts/policycosts_tmp.tex

\begin{document}
\begin{frontmatter}
\title{Policy Costs \\ \pa{
Target Journals: Ecological Applications, Journal of Applied Ecology, some discussion of whether scope for PNAS}}
\author[cpb]{C. Boettiger\corref{cor1}}
\ead{cboettig@ucdavis.edu}
\author[melbourne]{M. Bode}
\author[esp]{J. N. Sanchirico}
\author[utk-econ]{J. LaRiviere}
\author[cpb,esp]{A.M. Hastings}
\author[utk-eeb]{P. R Armsworth}
\cortext[cor1]{Corresponding author, present address: XXX}
\address[cpb]{Center for Population Biology, University of California, Davis, California 95616, USA}
\address[melbourne]{Australian Research Council Centre of Excellence for Environmental Decisions, University of Melbourne, School of Botany,
Parkville, Melbourne, VIC 3010, Australia}
\address[esp]{Department of Environmental Science \& Policy, University of California, Davis, CA 95616, USA}
\address[utk-econ]{Department of Economics, University of Tennessee, Knoxville, TN 37996, USA}
\address[utk-eeb]{Department of Ecology and Evolutionary Biology, University of Tennessee, Knoxville, TN 37996, USA}

\begin{abstract}
\cdb{Carl's comments \& questions added in green} \\
\pa{Paul's comments \& questions added in blue} \\
\jr{Jake's comments \& questions added in red}
\end{abstract}
\begin{keyword}
  optimal control \sep management \sep stochastic dynamic programming \sep fisheries 
\end{keyword}

@@

\begin{figure}[ht]
  \begin{center}
    \subfigure[Optimal Policy]{\includegraphics[width=.5\textwidth]{figure/optimal_harvest}\label{fig:1a}}
    \subfigure[Typical Policy]{\includegraphics[width=.5\textwidth]{figure/typical_policy}\label{fig:1b}}
  \end{center}
  \caption{\ref{fig:1a} shows a typical solution found by an optimal
  control solution by stochastic dynamic programming for the optimal catch
  quota in a managed fishery.  Note that the solution tends to track the
  noise, resulting in a highly variable policy.  \ref{fig:1b} shows the
  actual quotas set over the past decade for Bluefin tuna, which show
  great intertia to change despite considerable movement in the stock
  dynamics.  \cdb{Conceptual picture illustrating the need to account
  for costs to changing policy. Current images are just placeholders.
  B should be replaced with real data, perhaps tuna quotas from Paul.
  Should stock dynamics actually be shown?}}
  \label{fig:1}
\end{figure}

@@

\pa{
 Problem description resolved in Meeting 3 - note the list of possible causal mechanisms here (reaching agreement to processor plants) was negotiated with some not being acceptable suggestions:

@@

\pa{

@@

\pa{
Resolved in Meeting 3: We will only do comparisons described last time as $L_1$, $L_2$ and fixed. They have new and more descriptive names now. $c_0>0$ in all comparisons please. We do not present the asymmetric comparison.

@@

\pa{
  Suggested from Meeting 3:

@@

\jr{

@@

\jr{
The fact that there is no uniform metric for comparing different functional forms of the penalty function complicates identifying the implications of various penalty functions on optimal management.  Put another way, it is unclear what parameter values should be used for each functional form in order to compare the relative effect of each penalty function on optimal management.  
To address this issue, consider the following rule for comparing functional forms inspired by Bovenberg, Goulder and Gurnery (2005) and Bovenberg, Goulder and Jacobsen (2008).  By definition, adding a constraint, in the form of a penalty function, to the social planner’s objective function will reduce the NPV of the resource in addition to affecting the optimal management policy.  For example, each individual penalty function equation (3)-(6) is multiplied by a constant C2.  As the magnitude of the penalty function increases (e.g., C2 increases), the NPV value of the resource decreases.  Importantly, though, the rate at which the NPV is affected by a given increase in magnitude of the penalty function is different for different penalty functions.  One way to compare the relative impact of penalty functions on optimal management is to choose parameters for the penalty function that imply the same level of NPV conditional on optimal management.

@@

Figure~\ref{fig:shapes} shows the impact the adjustment cost has on the optimal policy.   Each panel is generated against the same sequence of random shocks so that they can be compared directly.  In each case, the optimal solution without any adjustment cost is shown in black and the policy induced by optimization under the given adjustment penalty is overlaid in blue.  The $L_1$ panel of Figure~\ref{fig:shapes} shows a pattern typical of the $L_1$-norm, which tends to avoid small adjustments to the policy, resulting in long periods of constant policy followed by sudden bursts of adjustment. This results in a relatively step-like policy pattern.  In contrast, the $L_2$-norm tracks all of the changes made by the cost-free policy, but with smaller magnitude.  This results in a smoother curve that undershoots the larger oscillations seen in the cost-free optimum, but results in a policy that changes incrementally each interval.  The fixed fee only makes large adjustments $L_1$, as expected where the adjustment magnitude does not impact the cost.  Where the $L_1$ norm attempts to accomidate the large oscillations at the end with a constant quota in between the extremes, the fixed cost takes the opposite approach of one very large swing.  Asymmetric ($L_1$) adjustment costs attempt to track the optimal solution, and can end up with larger fees than anticipated.  \cdb{Not quite sure why we get this pattern in the asymmetrics!}

@@

\cdb{ In terms of a policy set on escapement instead of harvest, our solutions are actually more volatile than~\citet{Reed1979}.  Maybe this leads to a discussion of what the control policy should be defined in terms of (i.e. catch vs escapement)?  Surely the simplicity of the constant-escapement rule has led to it's popularity in some part due because that simplicity avoids adjustment costs?  We should consider a parameter range where the solution has less chatter?  Parameters that actually satisify the \citet{Reed1979} self-sustaining condition?}

@@

\pa{ 
  Figure 3 stays largely as is.  But we also need to see the corresponding x trajectories in a way that makes for easy comparisons but not cluttered axes
}

@@

\pa{ 
 A version of Figure 4 to go in. But limit the range of the fraction on the horizontal axis more.  We need to see the corresponding variance and autocorrelation for x as well as h. Also suggested we might want a panel showing cross-correlation statistic as well x to h variation although depending on what it shows it could perhaps go to SI.
}

The comparisons shown in Figure~\ref{fig:shapes} are made at a fixed magnitude of the policy cost equal to 25\% of the net present value derived from the cost-free optimal strategy. The different functional forms may also respond differently to an increasing magnitude of the adjustment cost.  To quantify the extent to which the policy cost decreases the volatility of the proposed policy, we calculate the variance in the fishing quota over time under each policy. The variance is averaged over 50 replicates, and recalculated at each of 20 different intensities ranging from 0 (no cost) to 1 (NPV reduced to zero by the adjustment costs)The variance is averaged over 50 replicates, and recalculated at each of 20 different intensities ranging from 0 (no cost) to 1 (NPV reduced to zero, by the adjustment costs), shown in Figure~\ref{fig:summarystats}. \cdb{Correction: not actually zero, just to max reduction (usually what is obtained by constant quota).  Should indicate where this asymptote has occurred)}.

@@

\cdb{Add additional plot: Is value a linear function of policy cost, or is there a sharp transition? }
\pa{ Must be nonlinear somewhere when adjustment costs exceed profits? }

@@

\begin{figure}
  \begin{center}
    \subfigure[L1]{\includegraphics[width=.45\textwidth]{figure/7751440758_99645d6e5a_o.png}\label{fig:L1cost}}
    \caption{Ignoring the cost of policy adjustment results in greater profits from fishing, but even greater costs for adjusting the harvest quotas each year.  Costs and profits are shown for ignoring the adjustment costs (Reed solution, purple and blue) and accounting for the adjustment (green and red).  \cdb{Though only L1 shown for the moment, would probably show all four types.  Possibly a table or box-and-whiskers style plot would be better?}}\label{fig:profits_costs}
  \end{center}
\end{figure}

\pa{ Keep Figure 5 or its equivalent for one penalty function formulation and talk through what it means and how to interpret it.

@@

\begin{figure}
 \begin{center}
 \subfigure[L1]{\includegraphics[width=.45\textwidth]{figure/7751440918_3b54ff2397_o.png}\label{fig:L1npv_dist}}
 \caption{\textbf{The impact of ignoring policy costs}.  Distribution of net present value realized over 100 simulations when adjustment costs are ignored (blue), compared to when adjustment costs are optimally accounted for (red). \cdb{Though only L1 shown for the moment, would probably show all four types.  Possibly a table or box-and-whiskers style plot would be better?}}\label{fig:npv_dist}
 \end{center}
\end{figure}

@@

\cdb{\textbf{Further things to look at?}
\begin{itemize}
  \item How are costs partitioned between policy adjustments and deviation from optimality? 
  \item Risk sensitivity: does policy inertia increase or decrease extinction risk? Does accounting for the policy cost increase or decrease extinction risk?  (only in cases where extinction is possible: \emph{e.g.} in large variance, outside of Reed's self-sustaining range.  Or Allee model)
\end{itemize}
}

\section{Discussion}
\cdb{Some possible things to discuss: could add others, could remove some.}
\begin{itemize}
\item From Meeting 3: Interest in how the inclusion of these costs would operationally put a population at greater risk of extinction (e.g. if including the transaction costs increases the variance and autocorrelation of N when subject to the optimal policy). Should expect this, because (AH) as the transaction costs become infinite, you would never change your policy which puts you in the world of open loop control; TAC fixed for all time, which we know puts the stock at greater risk of extinction.
\item Alan on the Table looking at the impacts of $\sigma_{\epsilon}$ should flag that might also be good to look at autocorrelated environmental noise and how that affects thing. Here we look at how the optimal policy induces more color in the stock size EVEN though the environmental variability going into it is white noise.
\item (JL) Interpreting  (1), (2), (3), and (4) in terms of how much you would have available to pay the Japanese and Canadians to convince them to participate in an expedited process to change TACs.
\item   Comparison of the optimal policy solution to the Reed model, traditional economic smoothing penalty - which now appears in SI
\item  Comparison between the different functional forms -- smoothing (L2)
  non-smoothing (L1), and de-stablizing (fixed).
\item   Induced costs (relative to free adjustment) vs direct costs (paid for adjusting) 
%\item   Impact of symmetric vs asymmetric costs
\item   Contrast steady-state results to dynamic solutions under stochastic shocks.
\end{itemize}

>>>>

\begin{document}
\begin{frontmatter}
\title{Policy Costs }
\author[cpb]{C. Boettiger\corref{cor1}}
\ead{cboettig@ucdavis.edu}
\author[melbourne]{M. Bode}
\author[esp]{J. N. Sanchirico}
\author[utk-econ]{J. LaRiviere}
\author[cpb,esp]{A.M. Hastings}
\author[utk-eeb]{P. R Armsworth}
\cortext[cor1]{Corresponding author, present address: XXX}
\address[cpb]{Center for Population Biology, University of California, Davis, California 95616, USA}
\address[melbourne]{Australian Research Council Centre of Excellence for Environmental Decisions, University of Melbourne, School of Botany,
Parkville, Melbourne, VIC 3010, Australia}
\address[esp]{Department of Environmental Science \& Policy, University of California, Davis, CA 95616, USA}
\address[utk-econ]{Department of Economics, University of Tennessee, Knoxville, TN 37996, USA}
\address[utk-eeb]{Department of Ecology and Evolutionary Biology, University of Tennessee, Knoxville, TN 37996, USA}

\begin{abstract}
\end{abstract}
\begin{keyword}
  optimal control \sep management \sep stochastic dynamic programming \sep fisheries 
\end{keyword}

@@

\begin{figure}[ht]
  \begin{center}
    \subfigure[Optimal Policy]{\includegraphics[width=.5\textwidth]{figure/optimal_harvest}\label{fig:1a}}
    \subfigure[Typical Policy]{\includegraphics[width=.5\textwidth]{figure/typical_policy}\label{fig:1b}}
  \end{center}
  \caption{\ref{fig:1a} shows a typical solution found by an optimal
  control solution by stochastic dynamic programming for the optimal catch
  quota in a managed fishery.  Note that the solution tends to track the
  noise, resulting in a highly variable policy.  \ref{fig:1b} shows the
  actual quotas set over the past decade for Bluefin tuna, which show
  great intertia to change despite considerable movement in the stock
  dynamics.  {\color{green}Conceptual picture illustrating the need to account
  for costs to changing policy. Current images are just placeholders.
  B should be replaced with real data, perhaps tuna quotas from Paul.
  Should stock dynamics actually be shown?}}
  \label{fig:1}
\end{figure}

@@

{\color{blue}
 Problem description resolved in Meeting 3 - note the list of possible causal mechanisms here (reaching agreement to processor plants) was negotiated with some not being acceptable suggestions:

@@

{\color{blue}

@@

{\color{blue}
Resolved in Meeting 3: We will only do comparisons described last time as $L_1$, $L_2$ and fixed. They have new and more descriptive names now. $c_0>0$ in all comparisons please. We do not present the asymmetric comparison.

@@

{\color{blue}
  Suggested from Meeting 3:

@@

{\color{red}

@@

{\color{red}
The fact that there is no uniform metric for comparing different functional forms of the penalty function complicates identifying the implications of various penalty functions on optimal management.  Put another way, it is unclear what parameter values should be used for each functional form in order to compare the relative effect of each penalty function on optimal management.  
To address this issue, consider the following rule for comparing functional forms inspired by Bovenberg, Goulder and Gurnery (2005) and Bovenberg, Goulder and Jacobsen (2008).  By definition, adding a constraint, in the form of a penalty function, to the social planner’s objective function will reduce the NPV of the resource in addition to affecting the optimal management policy.  For example, each individual penalty function equation (3)-(6) is multiplied by a constant C2.  As the magnitude of the penalty function increases (e.g., C2 increases), the NPV value of the resource decreases.  Importantly, though, the rate at which the NPV is affected by a given increase in magnitude of the penalty function is different for different penalty functions.  One way to compare the relative impact of penalty functions on optimal management is to choose parameters for the penalty function that imply the same level of NPV conditional on optimal management.

@@

Figure~\ref{fig:shapes} shows the impact the adjustment cost has on the optimal policy.   Each panel is generated against the same sequence of random shocks so that they can be compared directly.  In each case, the optimal solution without any adjustment cost is shown in black and the policy induced by optimization under the given adjustment penalty is overlaid in blue.  The $L_1$ panel of Figure~\ref{fig:shapes} shows a pattern typical of the $L_1$-norm, which tends to avoid small adjustments to the policy, resulting in long periods of constant policy followed by sudden bursts of adjustment. This results in a relatively step-like policy pattern.  In contrast, the $L_2$-norm tracks all of the changes made by the cost-free policy, but with smaller magnitude.  This results in a smoother curve that undershoots the larger oscillations seen in the cost-free optimum, but results in a policy that changes incrementally each interval.  The fixed fee only makes large adjustments $L_1$, as expected where the adjustment magnitude does not impact the cost.  Where the $L_1$ norm attempts to accomidate the large oscillations at the end with a constant quota in between the extremes, the fixed cost takes the opposite approach of one very large swing.  Asymmetric ($L_1$) adjustment costs attempt to track the optimal solution, and can end up with larger fees than anticipated.  {\color{green}Not quite sure why we get this pattern in the asymmetrics!}

@@

{\color{green} In terms of a policy set on escapement instead of harvest, our solutions are actually more volatile than~\citet{Reed1979}.  Maybe this leads to a discussion of what the control policy should be defined in terms of (i.e. catch vs escapement)?  Surely the simplicity of the constant-escapement rule has led to it's popularity in some part due because that simplicity avoids adjustment costs?  We should consider a parameter range where the solution has less chatter?  Parameters that actually satisify the \citet{Reed1979} self-sustaining condition?}

@@

{\color{blue} 
  Figure 3 stays largely as is.  But we also need to see the corresponding x trajectories in a way that makes for easy comparisons but not cluttered axes
}

@@

{\color{blue} 
 A version of Figure 4 to go in. But limit the range of the fraction on the horizontal axis more.  We need to see the corresponding variance and autocorrelation for x as well as h. Also suggested we might want a panel showing cross-correlation statistic as well x to h variation although depending on what it shows it could perhaps go to SI.
}

The comparisons shown in Figure~\ref{fig:shapes} are made at a fixed magnitude of the policy cost equal to 25\% of the net present value derived from the cost-free optimal strategy. The different functional forms may also respond differently to an increasing magnitude of the adjustment cost.  To quantify the extent to which the policy cost decreases the volatility of the proposed policy, we calculate the variance in the fishing quota over time under each policy. The variance is averaged over 50 replicates, and recalculated at each of 20 different intensities ranging from 0 (no cost) to 1 (NPV reduced to zero by the adjustment costs)The variance is averaged over 50 replicates, and recalculated at each of 20 different intensities ranging from 0 (no cost) to 1 (NPV reduced to zero, by the adjustment costs), shown in Figure~\ref{fig:summarystats}. {\color{green}Correction: not actually zero, just to max reduction (usually what is obtained by constant quota).  Should indicate where this asymptote has occurred)}.

@@

{\color{green}Add additional plot: Is value a linear function of policy cost, or is there a sharp transition? }
{\color{blue} Must be nonlinear somewhere when adjustment costs exceed profits? }

@@

\begin{figure}
  \begin{center}
    \subfigure[L1]{\includegraphics[width=.45\textwidth]{figure/7751440758_99645d6e5a_o.png}\label{fig:L1cost}}
    \caption{Ignoring the cost of policy adjustment results in greater profits from fishing, but even greater costs for adjusting the harvest quotas each year.  Costs and profits are shown for ignoring the adjustment costs (Reed solution, purple and blue) and accounting for the adjustment (green and red).  {\color{green}Though only L1 shown for the moment, would probably show all four types.  Possibly a table or box-and-whiskers style plot would be better?}}\label{fig:profits_costs}
  \end{center}
\end{figure}

{\color{blue} Keep Figure 5 or its equivalent for one penalty function formulation and talk through what it means and how to interpret it.

@@

\begin{figure}
 \begin{center}
 \subfigure[L1]{\includegraphics[width=.45\textwidth]{figure/7751440918_3b54ff2397_o.png}\label{fig:L1npv_dist}}
 \caption{\textbf{The impact of ignoring policy costs}.  Distribution of net present value realized over 100 simulations when adjustment costs are ignored (blue), compared to when adjustment costs are optimally accounted for (red). {\color{green}Though only L1 shown for the moment, would probably show all four types.  Possibly a table or box-and-whiskers style plot would be better?}}\label{fig:npv_dist}
 \end{center}
\end{figure}

@@

{\color{green}\textbf{Further things to look at?}
\begin{itemize}
  \item How are costs partitioned between policy adjustments and deviation from optimality? 
  \item Risk sensitivity: does policy inertia increase or decrease extinction risk? Does accounting for the policy cost increase or decrease extinction risk?  (only in cases where extinction is possible: \emph{e.g.} in large variance, outside of Reed's self-sustaining range.  Or Allee model)
\end{itemize}
}

\section{Discussion}
{\color{green}Some possible things to discuss: could add others, could remove some.}
\begin{itemize}
\item From Meeting 3: Interest in how the inclusion of these costs would operationally put a population at greater risk of extinction (e.g. if including the transaction costs increases the variance and autocorrelation of N when subject to the optimal policy). Should expect this, because (AH) as the transaction costs become infinite, you would never change your policy which puts you in the world of open loop control; TAC fixed for all time, which we know puts the stock at greater risk of extinction.
\item Alan on the Table looking at the impacts of $\sigma_{\epsilon}$ should flag that might also be good to look at autocorrelated environmental noise and how that affects thing. Here we look at how the optimal policy induces more color in the stock size EVEN though the environmental variability going into it is white noise.
\item (JL) Interpreting  (1), (2), (3), and (4) in terms of how much you would have available to pay the Japanese and Canadians to convince them to participate in an expedited process to change TACs.
\item   Comparison of the optimal policy solution to the Reed model, traditional economic smoothing penalty - which now appears in SI
\item  Comparison between the different functional forms -- smoothing (L2)
  non-smoothing (L1), and de-stablizing (fixed).
\item   Induced costs (relative to free adjustment) vs direct costs (paid for adjusting) 
%\item   Impact of symmetric vs asymmetric costs
\item   Contrast steady-state results to dynamic solutions under stochastic shocks.
\end{itemize}
